---
title: "Homework 8"
author: "Chris Gahagan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
# the code below controls the default settings for each chunk
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center", 
                      fig.height=3, 
                      fig.width=5)
knitr::opts_knit$set("root.dir")

# load packages here, so they don't show up in and clutter the document
library(tidyverse)
library(haven)
library(kableExtra)
library(ggplot2)
library(ggrepel)
```

# Chapter 8 Scatter Plots
## Exercise 8.1
### Clark and Golder Script
```{r fig.height=3, fig.width=5}
parties<- read_rds("data/parties.rds") 
ggplot(parties, aes(x = eneg, y = enep)) + 
  geom_point()+
  facet_wrap(vars(electoral_system))
```

## Exercise 8.2
### Uninsured voters ACA favorability by Governor's Position and Poverty Level
```{r fig.height=3, fig.width=5}
politics<-read.csv("data/politics_and_need.csv")
ggplot(politics, aes(x = percent_uninsured, y = percent_favorable_aca, color = percent_poverty)) + 
  geom_point()+
facet_wrap(vars(gov_position))
```

## Exercise 8.3
### 8.3.1 Geom_text() plot
```{r fig.height=3, fig.width=5}
ggplot(politics, aes(x = percent_uninsured, y = percent_favorable_aca, label = state_abbr)) + 
  geom_text(alpha = .5)+
  facet_wrap(vars(gov_position))
```

### 8.3.2 Geom_label() plot
```{r fig.height=3, fig.width=5}
ggplot(politics, aes(x = percent_uninsured, y = percent_favorable_aca, label = state_abbr, 
                     color = state)) + 
  theme(legend.position = "none")+
  geom_label(alpha = .1)+
  facet_wrap(vars(gov_position))
```
### 8.3.3 Geom_text_repel() plot
```{r fig.height=3, fig.width=5}
ggplot(politics, aes(x = percent_uninsured, y = percent_favorable_aca, label = state_abbr,
                     color = state)) + 
  theme(legend.position = "none")+
  geom_point(alpha = .1)+
  geom_text_repel()+
  facet_wrap(vars(gov_position))
```
### 8.3.4 Geom_label_repel() plot
```{r fig.height=3, fig.width=5}
ggplot(politics, aes(x = percent_uninsured, y = percent_favorable_aca, label = state_abbr, 
                     color = state)) + 
  theme(legend.position = "none")+
  geom_point(alpha = .1)+
  geom_label_repel()+
  facet_wrap(vars(gov_position))
```

# Chapter 9 Correlation Coefficient
## Exercise 9.4 Gamson Correlation Data and Plot
```{r fig.height=3, fig.width=5}
gamson<-read_rds("data/gamson.rds") #loading gamson
glimpse(gamson)

cor_df<-gamson%>% #creating correlation data
  summarise(cor = cor(seat_share, portfolio_share))
glimpse(cor_df)

ggplot(gamson, aes(x = seat_share, y = portfolio_share)) + 
  geom_point(alpha = .5)+
geom_label(data = cor_df, aes(x = Inf, y = Inf, label = paste0("cor = ", round(cor, 2))),
           hjust = 1.1, vjust = 1.1)+
  theme_bw() #plotting correlation data
```

## Exercise 9.5
### 9.5.1 

```{r}
devtools::install_github("pos5737/pos5737data")
data(anscombe, package = "pos5737data")

smry_ans <- anscombe %>%
group_by(dataset) %>%
summarize(cor = cor(x = x, 
                      y = y))%>%
glimpse()
```
1. **All four sets have almost identical correlation**
1. **The data sets each suggest a strong relationship between x and y**

### 9.5.2 Plots of anscombe
```{r fig.height=3, fig.width=5}
ggplot(anscombe, aes(x = x, y = y)) + 
  geom_point() + 
  facet_wrap(vars(dataset))
```
1. **All the plots are completely different from one another.**
1. **For the amount of data, there seems to be a positive relationship between X and Y, except for in Panel IV, and Panel II the data looks like it is starting to turn negative.**
1. **No, just the correlation coefficient alone did not offer a good summary at all comparably.**
