---
title: "Homework 8"
author: "Chris Gahagan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
# the code below controls the default settings for each chunk
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center", 
                      fig.height=3, 
                      fig.width=5)

# load packages here, so they don't show up in and clutter the document
library(tidyverse)
library(haven)
library(kableExtra)
```


# Exercise 1.1

For this exercise, I was careful to **style** my *text* so that it was easy to read.

Where possible, I...

1. answered with
1. numbered lists.

Where appropriate, I...

- answered with
- bulleted lists. 

I formatted my `inline code` correctly and I used

# Headers, 

## Subheaders, and 

### Subsubheaders 

to organize my work.

I even used LaTeX equations, like $y = mx + b$, where needed.

I quoted authorities on the topic:

> "Always scatterplot your data."  ---Carlisle Rainey

**Most importantly**, I used R code chunks to include code, output, and figures in the document without copy-and-pasting.

```{r, fig.height=2.5, fig.width=4}
parties <- read_rds("data/parties.rds")

ggplot(parties, aes(x = eneg, y = enep)) + 
  geom_point()
```

Notice how I overrode the `fig.height` and the `fig.width` I set as the default in the initial code chunk above. Here's a bit more discussion about Exercise 1.1. 


## Exercise 2.3

Here's another exercise...

```{r}
parties <- read_rds("data/parties.rds")

glimpse(parties)
```


